### 2021-05-04 yfcc100m/paper/vldb2021/submission/review_response/reviews_response.tex

\bigskip

\newpage
\section{Reviewer \#4}

\noindent %
\textbf{
D1. The proposed solution seems to use the functionalities of the existing systems
as it is. Authors should provide more original ideas or more innovative designs.
For example, providing optimizations that specifically target visual data or query
patterns associated could have been more meaningful to the research communities and
convince users to replace their customized solution to VDMS.
}\bigskip

We have provided additional details on which operations we support and our
decision for choosing the operations in section 3.
We also elaborated more on the benefits of
using VDMS over relational databases in Section 3.1.

@@

\bigskip
\noindent %
\textbf{
D3. The paper should detail the types of queries, and image preprocessing it supports,
as this being “one of the most differentiating aspects” as mentioned by them.
And for the selection of operations supported, authors need to argue for their
decision in the application contexts.
}\bigskip

Thank you for this recommendation.
We have provided additional details on which operations we support and our
decision for choosing the operations in section 3.

\bigskip
\noindent %
\textbf{
D4. Data scientists commonly perform data exploration on raw data and interactively
curate their datasets for downstream tasks like model training.
VDMS could design new mechanisms to support interactive analysis,
which would be beneficial.
}\bigskip

Interactive analysis is out of scope for this paper but this can easily be done
using the current implementation of VDMS.
To support interactive analysis, a new API/front-end could be implemented on top of
VDMS as a web app without adding any additional abstractions.
An example of such front-end can be found \url{http://coco.datasets.aperturedata.io}.
The front-end is very thin, as most of the heavy-load is done by VDMS through
the interfaces mentioned in this work
(plus a thin REST abstraction we have added recently).
In section 3 of final version, we briefly mention this ability.

@@

\bigskip
\noindent %
\textbf{
D5. In terms of scalability, the paper only shows that VDMS can handle large
datasets, yet it is not known how VDMS can scale horizontally with more
computation resources.
For more complex logic of image preprocessing, VDMS will suffer from its
single server capacity.
}\bigskip

Thanks for this comment.
We have included this capability in the "Future Work" section
added to the final version.

@@

\noindent %
\textbf{
D1: VDMS is a valuable contribution to Database systems where it takes
some first important steps to handle visual data as a first-class citizen
instead of considering it a blob of information. However, the description
of VDMS is rather short (only 4 pages), and some critical technical
details are missing. In particular, what are the technical challenges
for supporting ACID properties using the graph model abstraction? Are
the solutions analogous to RDBMS’s? Does VDMS also support crash
recovery like an RDBMS? What are the key challenges for implementing
the new visual object computations?
}\bigskip

Thank you for the comment.
In Section 3.2, we have expanded on the crash recovery of PMGD in
comparison to other graph databases.

\bigskip
\noindent %
\textbf{
D2: The coverage of persistent memory is underwhelming because persistent memory
is never used in the experiments.
What is the key advantage of using persistent memory and how is it
more suitable for visual data? Why not add experiments comparing VDMS with
and without using PMGD?
}\bigskip

We did not elaborate on advantages of using persistent memory or include
any PMGD experiments due to page limitations and the use of SSDs
instead of persistent memory in the evaluation.
PMGD performance evaluation will be published separately to highlight
the advantages of using persistent memory for visual data.

### 2021-05-04 yfcc100m/paper/vldb2021/design.tex
Cleaned some responses to reviewer
Update design section based on reviewer's comment

By providing the ability to store visual data objects together with
application-defined entities and its properties, VDMS can manage
all the data the application need behind a single, unified API.
This is in contrast with current applications that rely on a combination
of multiple data management systems and APIs to access different
portions of the data they need
\cite{tao, sculley2015hidden, mayer2020scalable, sculley2015hidden}.

@@

Listing~\ref{findimagegeo} shows another sample query, in this case, for retrieval.
In this particular example, the transaction retrieves all the images
of \textit{alligators} with probability higher than 0.66,
filter by latitude and longitude within 1 degree,
apply a resize operation to make the images 224x224,
rotate the images 45.34 degrees, and return the images as "png" files.
It is important to note how the API natively supports basic building
blocks of visual data processing, like resize, rotation, or transcoding
(changing output formats and encodings).
The API allows interaction with metadata, images, videos, bounding boxes,
frames, feature vectors, and more in a similar fashion,
and it is fully documented on the project's Github
wiki~\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description}.

>>>>

By providing the ability to store visual data objects together with
application-defined entities and its properties, VDMS can manage
all the data the application need behind a single, unified API.
This means users can access all data (metadata, images, videos, etc.)
from the VDMS API and even implement their own API/front-end on top
of VDMS without adding any additional abstractions.
This is in contrast with current applications that rely on a combination
of multiple data management systems and APIs to access different
portions of the data they need
\cite{tao, sculley2015hidden, mayer2020scalable, sculley2015hidden}.

@@

Listing~\ref{findimagegeo} shows another sample query, in this case, for retrieval.
In this particular example, the transaction retrieves all the images
of \textit{alligators} with probability higher than 0.66,
filter by latitude and longitude within 1 degree,
apply a resize operation to make the images 224x224,
rotate the images 45.34 degrees, and return the images as "png" files.
It is important to note how the API natively supports basic building
blocks of visual data processing, like resize, rotation, or transcoding
(changing output formats and encodings).
Moreover, because VDMS is in control of the metadata and the image data,
re-ordering or pre-processing operations can be done transparently,
increasing the performance of the retrieval process.
The API allows interaction with metadata, images, videos, bounding boxes,
frames, feature vectors, and more in a similar fashion,
and it is fully documented on the project's Github
wiki~\footnote{https://github.com/IntelLabs/vdms/wiki/API-Description}.
The visual data pre-processing operations supported in VDMS are generic and
application independent.
By design, we only include pre-processing operations that are not specific
to one domain, but rather general for visual analytics.
